### 2018-05-03 papers/synth/intro.tex
intro improve

%Motivate VTS

Eukaryotic cells, including human cells, consist of multiple membrane bound compartments.
Material is transported among these compartments by the vesicle transport system (VTS) []. Briefly,
the source compartment produces a membrane bound packet of molecules called a vesicle. After
release, this vesicle specifically recognizes the correct target compartment within the cell, and fuses
with it. The molecules that form the machinery of the VTS are known. We also know a lot about the
specific functions of these molecules and how these molecules interact amongst each other. In spite
of this detailed knowledge at the level of the molecules, the structure of the VTS network, or the
road-map of the eukaryotic cell, is far from complete. The current knowledge of the network is put
together from a patch work of biological experiments. This information is scattered across several
publications. Even after this information is collected and put together, we find that the network
obtained is still not complete; new vesicles and new contents in previously known vesicles are
constantly being discovered. The synthesis for the unknown pieces may be assisted by computation
on the graph model of VTSs. 
% 
In this work, we use a model described in [] to find out, given a partial
VTS graph and details about interactions amongst its molecules, what the complete graph of the
VTS could look like. (Please look at appendix A for the detailed discussion on pros and cons of the
model.
%
%Eukaryotic cells, including human cells, consists of multiple compartments.
%
%Vesicle Traffic Systems(VTSs) are the material transport mechanisms among the compartments inside the cells~\cite{vtsIntro}.
%
%Almost all subsystems of the cells depend on VTSs.
\ashu{Restructure and connect to next line take the above into consideration}

%
Therefore, understanding how VTSs functions is one of the key
questions of cell biology.
%
In this paper, we are looking at the computational questions 
arise from the VTSs.
%
In the following, we use the model of VTSs that has been presented
in~\cite{VTS}.
%
Please look at appendix~\ref{sec:model}
for the detailed discussion on pros and cons of the model.

@@

% Partial info defence
%
Although the VTSs are important, our understanding of VTSs are partial.
%
It largely means that the current knowledge is due to the patch work
of biological experiments~\cite{model} for identifying the compartments,
channels, molecules, and their activity and regulatory control.
%
Often the information is scattered around in several publications.
%
Even after with some effort we may collate all the known information about
a VTS, we may still have unknown pieces of the system.
%
%{Speculative: Make a case for completing partial parts of VTSs!!}
%
For example, we may suspect that some edges may not have been
discovered in a VTS that does not satisfy the stability condition.
%
The synthesis for the unknown pieces may be {\em assisted} by computation on
the graph model of VTSs.
%

In this paper, we consider several versions of the synthesis problem
involving different parts of VTSs that can be synthesized, such as
modifying labels, adding/deleting edges, and learning activity functions.
%
We also consider variation on the properties against which we do synthesis,
namely stability, and $k$-connectedness that states
that VTS remains connected after removing any $k-1$ edges.
%
In order to synthesize the parts of a VTS such that it satisfies the
constraints, we encode the synthesis problem into a satisfiability of
quantified Boolean formulas(QBFs). 
%

>>>>

%Motivate VTS
\ashu{Reduce the intro by half page}

Eukaryotic cells, including human cells, consist of multiple membrane bound compartments.
Material is transported among these compartments by the vesicle transport system (VTS) []. Briefly,
the source compartment produces a membrane bound packet of molecules called a vesicle. After
release, this vesicle specifically recognizes the correct target compartment within the cell, and fuses
with it. The molecules that form the machinery of the VTS are known. \todo{connect to function }{We also know a lot about the specific functions} of these molecules and how these molecules interact amongst each other. In spite of this detailed knowledge at the level of the molecules, the structure of the VTS network, or the road-map of the eukaryotic cell, is far from complete. 
%The current knowledge of the network is put together from a patch work of biological experiments. This information is scattered across several publications. Even after this information is collected and put together, we find that the network obtained is still not complete; new vesicles and new contents in previously known vesicles are constantly being discovered. The synthesis for the unknown pieces may be assisted by computationon the graph model of VTSs. 
% 
%In this work, we use a model described in [] to find out, given a partial
%VTS graph and details about interactions amongst its molecules, what the complete graph of the
%VTS could look like. (Please look at appendix A for the detailed discussion on pros and cons of the
%model.
%
%Eukaryotic cells, including human cells, consists of multiple compartments.
%
%Vesicle Traffic Systems(VTSs) are the material transport mechanisms among the compartments inside the cells~\cite{vtsIntro}.
%
%Almost all subsystems of the cells depend on VTSs.
%
%Therefore, understanding how VTSs functions is one of the key
%questions of cell biology.
%
In this paper, we are looking at the computational questions 
arise from the VTSs.
%
In the following, we use the model of VTSs that has been presented
in~\cite{VTS}.
%
Please look at appendix~\ref{sec:model}
for the detailed discussion on pros and cons of the model.

@@

% Partial info defence
%
Although the VTSs are important, our understanding of VTSs are partial.
%
It largely means that the current knowledge is due to the patch work
of biological experiments~\cite{model} for identifying the compartments,
channels, molecules, and their activity and regulatory control.
%
Often the information is scattered around in several publications.
%
Even after with some effort we may collate all the known information about
a VTS, we may still have unknown pieces of the system; new vesicles and new contents in previously known vesicles are constantly being discovered.
%
%{Speculative: Make a case for completing partial parts of VTSs!!}
%
For example, we may suspect that some edges may not have been
discovered in a VTS that does not satisfy the stability condition.
%
The synthesis for the unknown pieces may be {\em assisted} by computation on
the graph model of VTSs.
%
In this paper, we consider several versions of the synthesis problem
involving different parts of VTSs that can be synthesized, such as
modifying labels, adding/deleting edges, and learning activity functions.
%
We also consider variation on the properties against which we do synthesis,
namely stability, and $k$-connectedness that states
that VTS remains connected after removing any $k-1$ edges.
%
In order to synthesize the parts of a VTS such that it satisfies the
constraints, we encode the synthesis problem into a satisfiability of
quantified Boolean formulas(QBFs). 
%
